Partitioned Local Depth (PaLD) Community Analyses in R

### 2025-02-03 2023-r-journal/dagostino-mcgowan.Rmd
update fig
update

The `community_clusters` function can be used to identify the community corresponding to each tissue sample. Since the output is a data frame, we can summarize the result using commonly employed R functions. For demonstration purposes, we will use the \CRANpkg{dplyr} package to summarize the community contributions.

```{r}
community_clusters(tissue_cohesion) |>
  dplyr::count(community, point)
```

From this, we can glean, for instance, that Community 1 consists of two types of tissue, the kidney and endometrium, Community 2 is comprised of only the hippocampus, etc. More informatively, we can display relationships between tissue samples, both locally and globally through the `plot_community_graphs` function  (Figure \ref{fig:fig4}). For clarity of the display, we show how to remove the labels using `show_labels = FALSE`. We will instead color according to the labels by passing these to the `vertex.color` argument for the `plot.igraph` function (via the `...` argument). Similarly, we can add a legend using the `legend()` function, as you would for an \CRANpkg{igraph} visualization. Additionally, we use the `edge_width_factor` and `emph_strong` arguments to adjust the width of the lines between and within PaLD communities.

@@

Note that while Community 1 does contain kidney and endometrium tissues, the respective sub-communities are well-separated. Of the 357 strong inter-community ties within Community 1, only three are between the two sub-communities. In fact, these are the only strong ties between different tissue types in the community cluster network (of 1064 total); a summary of community strong ties can be produced via the following code. Note that `tissue_graph_strong` is an \CRANpkg{igraph} object corresponding to the graph displayed in Figure \ref{fig:fig4}, restricted only to strong ties.

```{r}
tissue_graphs <- community_graphs(tissue_cohesion)
tissue_graph_strong <- tissue_graphs[["G_strong"]]
E <- igraph::get.edgelist(tissue_graph_strong)
table(apply(E, 1, paste, collapse = ","))
```

@@

This example explors a data set from \citet{dyen92} that summarizes relationships between 87 Indo-European languages from the perspective of cognates, coded using 2,655-dimensional binary vectors. A `dist` object was created from this data set and is included in the \CRANpkg{pald} package in an object called `cognate_dist`.

@@

We can then use the `neighbors` function from the \CRANpkg{igraph} package to extract the strong neighbors in this graph. For example, we can extract all neighbors for the language "French", via the followign code.

@@

Similarly, we can print the associated neighborhood weights by subsetting the cohesion matrix.

```{r}
cognate_cohesion["French", french_neighbors]
```

@@

We will contrast community analysis via PaLD to standard culuster analysis by considering two common clustering methods. The code below calculates the cohesion matrix (`exdata_cohesion`) as well as the community clusters obtained via PaLD (`exdata_pald`), along with clusters obtained via *k*-means (`exdata_kmeans`) and hierarchical clustering using complete linkage (`exdata_hclust`).

@@

This paper introduces the \CRANpkg{pald} package, demonstrating its utility for providing parameter-free community analysis which can easily be implemented for a variety of data sets, supplementing results from other methods for clustering, embedding, nearest neighbors, etc. Example code is provided advantages over other techniques are highlighted.

>>>>

We can display relationships between tissue samples, both locally and globally through the `plot_community_graphs` function  (Figure \ref{fig:fig4}). For clarity of the display, we show how to remove the labels using `show_labels = FALSE`. We will instead color according to the labels by passing these to the `vertex.color` argument for the `plot.igraph` function (via the `...` argument). Similarly, we can add a legend using the `legend()` function, as you would for an \CRANpkg{igraph} visualization. Additionally, we use the `edge_width_factor` and `emph_strong` arguments to adjust the width of the lines between and within PaLD communities.

@@

A summary of community strong ties can be produced via the following code. Note that `tissue_graph_strong` is an \CRANpkg{igraph} object corresponding to the graph displayed in Figure \ref{fig:fig4}, restricted only to strong ties.

<!-- The `community_clusters` function can be used to identify the community corresponding to each tissue sample. Since the output is a data frame, we can summarize the result using commonly employed R functions. For demonstration purposes, we will use the \CRANpkg{dplyr} package to summarize the community contributions. -->

<!-- ```{r} -->
<!-- community_clusters(tissue_cohesion) |> -->
<!--   dplyr::count(community, point) -->
<!-- ``` -->

<!-- From this, we can glean, for instance, that Community 1 consists of two types of tissue, the kidney and endometrium, Community 2 is comprised of only the hippocampus, etc. More informatively,  -->

```{r}
tissue_graphs <- community_graphs(tissue_cohesion)
tissue_graph_strong <- tissue_graphs[["G_strong"]]
E <- igraph::get.edgelist(tissue_graph_strong)
tissue_strong_ties <- data.frame(
  strong_ties = apply(E, 1, paste, collapse = ",")
)
tissue_strong_ties |>
  dplyr::count(strong_ties) |>
  dplyr::arrange(-n)
```

Note that there are only three strong ties between different tissue types (kidney and endometrium) in the community cluster network of 1,064 strong ties total.

@@

This example explores a data set from \citet{dyen92} that summarizes relationships between 87 Indo-European languages from the perspective of cognates, coded using 2,655-dimensional binary vectors. A `dist` object was created from this data set and is included in the \CRANpkg{pald} package in an object called `cognate_dist`.

@@

We can then use the `neighbors` function from the \CRANpkg{igraph} package to extract the strong neighbors in this graph. For example, we can extract all neighbors for the language "French", via the following code.

@@

Similarly, we can sort and print the associated neighborhood weights by subsetting the cohesion matrix.

```{r}
cognate_cohesion["French", french_neighbors] |>
  sort(decreasing = TRUE)
```

@@

We will contrast community analysis via PaLD to standard cluster analysis by considering two common clustering methods. The code below calculates the cohesion matrix (`exdata_cohesion`) as well as the community clusters obtained via PaLD (`exdata_pald`), along with $k=8$ clusters obtained via *k*-means (`exdata_kmeans`) and hierarchical clustering using complete linkage (`exdata_hclust`). Recall that there is no need to determine values for extraneous inputs in the case of PaLD (e.g. the number of clusters, as is necessary to specify for *k*-means and hierarchical clustering).

@@

This paper introduces the \CRANpkg{pald} package, demonstrating its utility for providing novel parameter-free community analysis which can easily be implemented for a variety of data sets, supplementing results from other methods for clustering, embedding, nearest neighbors, etc. Example code is provided along with discussion in the context of other commonly used R-based approaches.

### 2025-02-03 2023-r-journal/dagostino-mcgowan.tex
update

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 90d60fd UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 90d60fd (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
library(ggplot2)
ggplot(df, aes(x1, x2)) +
  geom_text(label = rownames(df)) + 
  coord_fixed(ratio = 1) + 
  xlim(c(4, 16)) + 
  ylim(c(4, 16))
\end{Sinput}
\begin{figure}
\includegraphics{dagostino-mcgowan_files/figure-latex/fig1-1} \caption[Visualization of the points from the data frame `df`]{Visualization of the points from the data frame `df`}\label{fig:fig1}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
plot_community_graphs(cohesion, 
                      vertex.label.cex = 2,
                      vertex.label.dist = 0.9)
\end{Sinput}
\begin{figure}
\includegraphics{dagostino-mcgowan_files/figure-latex/fig2-1} \caption[PaLD graph displaying the relationship between the points in data frame `df`]{PaLD graph displaying the relationship between the points in data frame `df`}\label{fig:fig2}
\end{figure}
\end{Schunk}

@@

plot_community_graphs(cohesion, 
                      layout = as.matrix(df),
                      vertex.size = 100,
                      vertex.label.color = "white",
                      axes = TRUE,
                      rescale = FALSE,
                      asp = 1,
                      xlim = c(4, 16),
                      ylim = c(4, 16))
\end{Sinput}
\begin{figure}
\includegraphics{dagostino-mcgowan_files/figure-latex/fig3-1} \caption[PaLD graph displaying the relationship between the points in data frame `df`, matching the original layout in Figure 1]{PaLD graph displaying the relationship between the points in data frame `df`, matching the original layout in Figure 1}\label{fig:fig3}
\end{figure}
\end{Schunk}

@@

The \texttt{community\_clusters} function can be used to identify the
community corresponding to each tissue sample. Since the output is a
data frame, we can summarize the result using commonly employed R
functions. For demonstration purposes, we will use the \CRANpkg{dplyr}
package to summarize the community contributions.

\begin{Schunk}
\begin{Sinput}
community_clusters(tissue_cohesion) |>
  dplyr::count(community, point)
\end{Sinput}
\begin{Soutput}
#>    community       point  n
#> 1          1 endometrium 15
#> 2          1      kidney 39
#> 3          2 hippocampus 31
#> 4          3  cerebellum 26
#> 5          4  cerebellum  1
#> 6          5       colon 33
#> 7          6       colon  1
#> 8          7       liver  7
#> 9          8  cerebellum  1
#> 10         9       liver 17
#> 11        10  cerebellum  2
#> 12        11       liver  2
#> 13        12  cerebellum  1
#> 14        13  cerebellum  4
#> 15        14  cerebellum  2
#> 16        15  cerebellum  1
#> 17        16    placenta  2
#> 18        17    placenta  1
#> 19        18    placenta  3
\end{Soutput}
\end{Schunk}

From this, we can glean, for instance, that Community 1 consists of two
types of tissue, the kidney and endometrium, Community 2 is comprised of
only the hippocampus, etc. More informatively, we can display
relationships between tissue samples, both locally and globally through
the \texttt{plot\_community\_graphs} function (Figure \ref{fig:fig4}).
For clarity of the display, we show how to remove the labels using
\texttt{show\_labels\ =\ FALSE}. We will instead color according to the
labels by passing these to the \texttt{vertex.color} argument for the
\texttt{plot.igraph} function (via the \texttt{...} argument).
Similarly, we can add a legend using the \texttt{legend()} function, as
you would for an \CRANpkg{igraph} visualization. Additionally, we use
the \texttt{edge\_width\_factor} and \texttt{emph\_strong} arguments to
adjust the width of the lines between and within PaLD communities.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{fig5} \caption[Community cluster network for the tissue data]{Community cluster network for the tissue data. The line colors indicate the PaLD communities; the point colors indicate the tissue classification.}\label{fig:fig4}
\end{figure}
\end{Schunk}

Note that while Community 1 does contain kidney and endometrium tissues,
the respective sub-communities are well-separated. Of the 357 strong
inter-community ties within Community 1, only three are between the two
sub-communities. In fact, these are the only strong ties between
different tissue types in the community cluster network (of 1064 total);
a summary of community strong ties can be produced via the following
code. Note that \texttt{tissue\_graph\_strong} is an \CRANpkg{igraph}
object corresponding to the graph displayed in Figure \ref{fig:fig4},
restricted only to strong ties.

\begin{Schunk}
\begin{Sinput}
tissue_graphs <- community_graphs(tissue_cohesion)
tissue_graph_strong <- tissue_graphs[["G_strong"]]
E <- igraph::get.edgelist(tissue_graph_strong)
table(apply(E, 1, paste, collapse = ","))
\end{Sinput}
\begin{Soutput}
#> 
#>   cerebellum,cerebellum             colon,colon endometrium,endometrium 
#>                     186                     241                      81 
#> hippocampus,hippocampus      kidney,endometrium           kidney,kidney 
#>                     191                       3                     273 
#>             liver,liver       placenta,placenta 
#>                      85                       4
\end{Soutput}
\end{Schunk}

@@

This example explors a data set from \citet{dyen92} that summarizes
relationships between 87 Indo-European languages from the perspective of
cognates, coded using 2,655-dimensional binary vectors. A \texttt{dist}
object was created from this data set and is included in the
\CRANpkg{pald} package in an object called \texttt{cognate\_dist}.

@@

We can then use the \texttt{neighbors} function from the
\CRANpkg{igraph} package to extract the strong neighbors in this graph.
For example, we can extract all neighbors for the language ``French'',
via the followign code.

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from aab3808:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

Similarly, we can print the associated neighborhood weights by
subsetting the cohesion matrix.

\begin{Schunk}
\begin{Sinput}
cognate_cohesion["French", french_neighbors]
\end{Sinput}
\begin{Soutput}
#>         Italian           Ladin       Provencal         Walloon French_Creole_C 
#>      0.01997696      0.02094596      0.02871174      0.03258771      0.02406057 
#> French_Creole_D         Spanish         Catalan 
#>      0.02406057      0.01679733      0.01859688
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{fig6} \caption[Community structure for 87 Indo-European languages, which employs cognate information that was coded via 2,665-dimensional binary vectors]{Community structure for 87 Indo-European languages, which employs cognate information that was coded via 2,665-dimensional binary vectors. Commonly identifiable language clusters arise along with informative inter- and intra-cluster structure. Several ancient languages are centrally located.}\label{fig:figlang}
\end{figure}
\end{Schunk}

@@

We will contrast community analysis via PaLD to standard culuster
analysis by considering two common clustering methods. The code below
calculates the cohesion matrix (\texttt{exdata\_cohesion}) as well as
the community clusters obtained via PaLD (\texttt{exdata\_pald}), along
with clusters obtained via \emph{k}-means (\texttt{exdata\_kmeans}) and
hierarchical clustering using complete linkage
(\texttt{exdata\_hclust}).

@@

\begin{Schunk}
\begin{Sinput}
par(mfrow = c(1, 3), pty = "s")
plot(
  exdata3,
  pch = 16,
  col = pald_colors[exdata_pald],
  xlab = "",
  ylab = "",
  main = "PaLD Communities",
  asp = 1
)
plot(
  exdata3,
  pch = 16,
  col = pald_colors[exdata_kmeans],
  xlab = "",
  ylab = "",
  main = "K-Means Clusters (k = 8)",
  asp = 1
)
plot(
  exdata3,
  pch = 16,
  col = pald_colors[exdata_hclust],
  xlab = "",
  ylab = "",
  main = "Hiearchical Clusters (k = 8)",
  asp = 1
)
\end{Sinput}
\begin{figure}
\includegraphics{dagostino-mcgowan_files/figure-latex/fig5-1} \caption[PaLD, k-means, and hierarchical 8-clustering of randomly generated example data (from \citet{berenhaut2022social}]{PaLD, k-means, and hierarchical 8-clustering of randomly generated example data (from \citet{berenhaut2022social}; Figure 4D).}\label{fig:fig5}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{fig7} \caption[Community structure for cultural distance data]{Community structure for cultural distance data.}\label{fig:figculture}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
dist_cohesion_plot(cultures, mutual = TRUE)
\end{Sinput}
\begin{figure}
\includegraphics{dagostino-mcgowan_files/figure-latex/figco-1} \caption{A plot of cohesion versus distance for the data. The identified communities are colored as in Figure \ref{fig:figculture}.}\label{fig:figco}
\end{figure}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 5de0378 UNW- 6 3 --
#> + attr: name (v/c), weight (e/n)
#> + edges from 5de0378 (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
library(ggplot2)
ggplot(df, aes(x1, x2)) +
  geom_text(label = rownames(df)) +
  coord_fixed(ratio = 1) +
  xlim(c(4, 16)) +
  ylim(c(4, 16))
\end{Sinput}
\begin{figure}[H]
\begin{center}
\includegraphics[width=5in]{dagostino-mcgowan_files/figure-latex/fig1-1} \caption[Visualization of the points from the data frame `df`]{Visualization of the points from the data frame `df`}\label{fig:fig1}
\end{center}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
plot_community_graphs(cohesion,
                      vertex.label.cex = 2,
                      vertex.label.dist = 0.9)
\end{Sinput}
\begin{figure}[H]
\includegraphics[width=5in,trim=0in 1in 0in 0.7in,clip]{dagostino-mcgowan_files/figure-latex/fig2-1} \caption[PaLD graph displaying the relationship between the points in data frame `df`]{PaLD graph displaying the relationship between the points in data frame `df`}\label{fig:fig2}
\end{figure}
\end{Schunk}

@@

plot_community_graphs(cohesion,
                      layout = as.matrix(df),
                      vertex.size = 100,
                      vertex.label.color = "white",
                      axes = TRUE,
                      rescale = FALSE,
                      asp = 1,
                      xlim = c(4, 16),
                      ylim = c(4, 16))
\end{Sinput}
\begin{figure}[H]
\includegraphics[width=5in,trim=0in 0.6in 0in 0.8in,clip]{dagostino-mcgowan_files/figure-latex/fig3-1} \caption[PaLD graph displaying the relationship between the points in data frame `df`, matching the original layout in Figure 1]{PaLD graph displaying the relationship between the points in data frame `df`, matching the original layout in Figure 1}\label{fig:fig3}
\end{figure}
\end{Schunk}

@@

We can display relationships between tissue samples, both locally and
globally through the \texttt{plot\_community\_graphs} function (Figure
\ref{fig:fig4}). For clarity of the display, we show how to remove the
labels using \texttt{show\_labels\ =\ FALSE}. We will instead color
according to the labels by passing these to the \texttt{vertex.color}
argument for the \texttt{plot.igraph} function (via the \texttt{...}
argument). Similarly, we can add a legend using the \texttt{legend()}
function, as you would for an \CRANpkg{igraph} visualization.
Additionally, we use the \texttt{edge\_width\_factor} and
\texttt{emph\_strong} arguments to adjust the width of the lines between
and within PaLD communities.

@@

\begin{Schunk}
\begin{figure}[H]
\includegraphics[width=5.5in,trim=0in 5in 0in 3in,clip]{fig5} \caption[Community cluster network for the tissue data]{Community cluster network for the tissue data. The line colors indicate the PaLD communities; the point colors indicate the tissue classification.}\label{fig:fig4}
\end{figure}
\end{Schunk}

A summary of community strong ties can be produced via the following
code. Note that \texttt{tissue\_graph\_strong} is an \CRANpkg{igraph}
object corresponding to the graph displayed in Figure \ref{fig:fig4},
restricted only to strong ties.

\begin{Schunk}
\begin{Sinput}
tissue_graphs <- community_graphs(tissue_cohesion)
tissue_graph_strong <- tissue_graphs[["G_strong"]]
E <- igraph::get.edgelist(tissue_graph_strong)
tissue_strong_ties <- data.frame(
  strong_ties = apply(E, 1, paste, collapse = ",")
)
tissue_strong_ties |>
  dplyr::count(strong_ties) |>
  dplyr::arrange(-n)
\end{Sinput}
\begin{Soutput}
#>               strong_ties   n
#> 1           kidney,kidney 273
#> 2             colon,colon 241
#> 3 hippocampus,hippocampus 191
#> 4   cerebellum,cerebellum 186
#> 5             liver,liver  85
#> 6 endometrium,endometrium  81
#> 7       placenta,placenta   4
#> 8      kidney,endometrium   3
\end{Soutput}
\end{Schunk}

Note that there are only three strong ties between different tissue
types (kidney and endometrium) in the community cluster network of 1,064
strong ties total.

@@

This example explores a data set from \citet{dyen92} that summarizes
relationships between 87 Indo-European languages from the perspective of
cognates, coded using 2,655-dimensional binary vectors. A \texttt{dist}
object was created from this data set and is included in the
\CRANpkg{pald} package in an object called \texttt{cognate\_dist}.

@@

We can then use the \texttt{neighbors} function from the
\CRANpkg{igraph} package to extract the strong neighbors in this graph.
For example, we can extract all neighbors for the language ``French'',
via the following code.

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from b09505b:
#> [1] Italian         Ladin           Provencal       Walloon
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

Similarly, we can sort and print the associated neighborhood weights by
subsetting the cohesion matrix.

\begin{Schunk}
\begin{Sinput}
cognate_cohesion["French", french_neighbors] |>
  sort(decreasing = TRUE)
\end{Sinput}
\begin{Soutput}
#>         Walloon       Provencal French_Creole_C French_Creole_D           Ladin
#>      0.03258771      0.02871174      0.02406057      0.02406057      0.02094596
#>         Italian         Catalan         Spanish
#>      0.01997696      0.01859688      0.01679733
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[H]
\includegraphics[width=5.5in,trim=0in 5in 0in 1in,clip]{fig6} \caption[Community structure for 87 Indo-European languages, which employs cognate information that was coded via 2,665-dimensional binary vectors]{Community structure for 87 Indo-European languages, which employs cognate information that was coded via 2,665-dimensional binary vectors. Commonly identifiable language clusters arise along with informative inter- and intra-cluster structure. Several ancient languages are centrally located.}\label{fig:figlang}
\end{figure}
\end{Schunk}

@@

We will contrast community analysis via PaLD to standard cluster
analysis by considering two common clustering methods. The code below
calculates the cohesion matrix (\texttt{exdata\_cohesion}) as well as
the community clusters obtained via PaLD (\texttt{exdata\_pald}), along
with \(k=8\) clusters obtained via \emph{k}-means
(\texttt{exdata\_kmeans}) and hierarchical clustering using complete
linkage (\texttt{exdata\_hclust}). Recall that there is no need to
determine values for extraneous inputs in the case of PaLD (e.g.~the
number of clusters, as is necessary to specify for \emph{k}-means and
hierarchical clustering).

@@

\begin{Schunk}
\begin{Sinput}
par(mfrow = c(1, 3), pty = "s")
plot(
  exdata3,
  pch = 16,
  col = pald_colors[exdata_pald],
  xlab = "",
  ylab = "",
  main = "PaLD Communities",
  asp = 1
)
plot(
  exdata3,
  pch = 16,
  col = pald_colors[exdata_kmeans],
  xlab = "",
  ylab = "",
  main = "K-Means Clusters (k = 8)",
  asp = 1
)
plot(
  exdata3,
  pch = 16,
  col = pald_colors[exdata_hclust],
  xlab = "",
  ylab = "",
  main = "Hiearchical Clusters (k = 8)",
  asp = 1
)
\end{Sinput}
\begin{figure}[H]
\includegraphics[width=5.5in,trim=0in 1in 0in 0.8in,clip]{dagostino-mcgowan_files/figure-latex/fig5-1} \caption[PaLD, k-means, and hierarchical 8-clustering of randomly generated example data (from \citet{berenhaut2022social}]{PaLD, k-means, and hierarchical 8-clustering of randomly generated example data (from \citet{berenhaut2022social}; Figure 4D).}\label{fig:fig5}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[H]
\includegraphics[width=5.5in,trim=0in 5in 0in 3in,clip]{fig7} \caption[Community structure for cultural distance data]{Community structure for cultural distance data.}\label{fig:figculture}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
dist_cohesion_plot(cultures, mutual = TRUE)
\end{Sinput}
\begin{figure}[H]
\includegraphics[width=5.5in,trim=0in 0.5in 0in 0.5in,clip]{dagostino-mcgowan_files/figure-latex/figco-1} \caption{A plot of cohesion versus distance for the data. The identified communities are colored as in Figure \ref{fig:figculture}.}\label{fig:figco}
\end{figure}
\end{Schunk}
